\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{hyperref}

\title{Software Requirements Specification (SRS)\\
AI Music Recommender System\\
Snapshot 1 - Core System}
\author{Project Group 5}
\date{\today}

\begin{document}
\maketitle

\section*{Version Description}
\begin{longtable}{p{2cm}p{9cm}p{3cm}}
\textbf{Version} & \textbf{Description} & \textbf{Date}\\ \hline
1.0 & Initial SRS for Snapshot 1 of the AI Music Recommender System. Core functionality: authentication, basic playback, interaction logging, and baseline recommendations. & \today\\
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This SRS defines the functional and non-functional requirements for Snapshot 1 of the AI Music Recommender System, which provides a minimal viable product for personalized music playback using basic user interaction data.

\subsection{Scope}
Snapshot 1 delivers a web or mobile application where users can register, authenticate, browse a catalog, play songs, provide like or skip feedback, and receive simple personalized recommendations based on their listening history.

\subsection{Intended Audience}
The intended audience includes the course instructor, teaching assistants, and project team members responsible for analysis, design, implementation, and testing of Snapshot 1.

\subsection{Overview}
This document describes external interfaces, functional requirements, non-functional requirements, and legal and ethical considerations limited to Snapshot 1 of the system.

\section{Overall Description}
\subsection{User Needs}
Users need:
\begin{itemize}
  \item A simple way to create an account and sign in securely.
  \item A music player to browse and play songs from a catalog.
  \item Personalized recommendations aligned with previous listening behavior.
  \item A means to express preferences (likes and skips) that influence future recommendations.
\end{itemize}

\subsection{Product Perspective}
The system is a standalone application with a client, backend server, and database layer. For Snapshot 1, the catalog is predefined and stored in the project database.

\section{External Interface Requirements}
\subsection{User Interface}
Snapshot 1 shall provide:
\begin{itemize}
  \item A login and registration screen for user authentication.
  \item A home screen that displays a list of recommended songs and basic playlists.
  \item A search screen to search by song title, artist, or genre.
  \item A now-playing screen with play, pause, next, and previous controls, plus like and skip buttons.
\end{itemize}

\subsection{Software Interfaces}
The client communicates with:
\begin{itemize}
  \item A backend API for registration, login, recommendation retrieval, catalog browsing, and interaction logging.
  \item A database storing user accounts, songs, artists, and interaction logs.
\end{itemize}

\subsection{Hardware Interfaces}
The system targets standard desktop or mobile devices with network connectivity and does not require special hardware.

\section{Functional Requirements}
\subsection{Authentication and User Management}
\begin{itemize}
  \item FR-1: The system shall allow a new user to create an account using email and password.
  \item FR-2: The system shall allow an existing user to log in with registered credentials.
  \item FR-3: The system shall validate credentials and reject invalid login attempts.
\end{itemize}

\subsection{Music Catalog and Playback}
\begin{itemize}
  \item FR-4: The system shall display a list of available songs with title, artist, and basic metadata.
  \item FR-5: The system shall allow a user to start playback of a selected song.
  \item FR-6: The system shall provide playback controls for play, pause, next, and previous.
\end{itemize}

\subsection{Recommendation and Interaction Logging}
\begin{itemize}
  \item FR-7: The system shall display a list of recommended songs on the home screen for the logged-in user.
  \item FR-8: The system shall allow users to like a currently playing song.
  \item FR-9: The system shall allow users to skip a song and automatically move to the next track.
  \item FR-10: The system shall log interactions, including plays, likes, and skips, associated with the user.
  \item FR-11: The system shall use the logged interactions to adjust future recommendations.
\end{itemize}

\subsection{Search}
\begin{itemize}
  \item FR-12: The system shall allow users to search for songs by title, artist, or genre.
  \item FR-13: The system shall return a list of matching songs that can be played.
\end{itemize}

\section{Non-Functional Requirements}
\subsection{Performance}
\begin{itemize}
  \item NFR-1: The system should load the home screen and recommended songs within a few seconds under normal network conditions.
\end{itemize}

\subsection{Usability}
\begin{itemize}
  \item NFR-2: Navigation among login, home, search, and now-playing screens shall be intuitive and consistent.
\end{itemize}

\subsection{Security}
\begin{itemize}
  \item NFR-3: Passwords shall be stored using secure hashing rather than plain text.
  \item NFR-4: Only authenticated users shall access personalized recommendations and interaction history.
\end{itemize}

\section{Legal and Ethical Considerations}
\subsection{Data Storage and Privacy}
The system stores user account information and listening history solely to provide and improve recommendations, limiting access to authorized components in the context of this educational project.

\subsection{User Consent}
Users are informed that their interaction data (likes, skips, and plays) is collected and used to personalize recommendations and is not shared with third parties.

\end{document}
