\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{hyperref}

\title{Software Requirements Specification (SRS)\\
AI Music Recommender System\\
Snapshot 4 - Final Release and Future Work}
\author{Project Group 5}
\date{\today}

\begin{document}
\maketitle

\section*{Version Description}
\begin{longtable}{p{2cm}p{9cm}p{3cm}}
\textbf{Version} & \textbf{Description} & \textbf{Date}\\ \hline
4.0 & Final SRS for Snapshot 4. Adds quick-mix feature, refinement requirements, and explicit future work. & \today\\
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This SRS finalizes requirements for Snapshot 4 by adding a quick-mix feature and documenting refinement, quality, and future work for the AI Music Recommender System.[web:13][web:14]

\subsection{Scope}
Snapshot 4 focuses on polishing existing functionality, adding a lightweight new feature, and clarifying requirements that improve usability and performance.

\section{New Functional Requirements}
\subsection{Quick Mix Feature}
\begin{itemize}
  \item FR-F1: The system shall provide a “Quick Mix” button that generates a mixed playlist using the user’s recent history, current mood (if any), and social signals.
  \item FR-F2: The system shall start playing the first track of the Quick Mix playlist automatically after it is generated.
\end{itemize}

\subsection{Refinement and Quality}
\begin{itemize}
  \item FR-F3: The system shall allow users to refresh a recommendation section (e.g., mood playlist, friends’ picks) to request a new set of songs.
  \item FR-F4: The system shall provide basic error messages and feedback when recommendation or network requests fail.
\end{itemize}

\section{Non-Functional Requirements (Snapshot 4)}
\subsection{Performance and Reliability}
\begin{itemize}
  \item NFR-F1: Generating a Quick Mix playlist shall complete within a few seconds under normal usage.
  \item NFR-F2: The system shall handle typical concurrent usage scenarios without noticeable degradation, within project constraints.
\end{itemize}

\subsection{Usability}
\begin{itemize}
  \item NFR-F3: Key actions (play, like, skip, mood change, Quick Mix) shall require at most a few taps or clicks from the main screen.
\end{itemize}

\section{Future Work}
Potential future improvements include:
\begin{itemize}
  \item Integration of more advanced machine learning models for music recommendation and mood detection.[web:13][web:16]
  \item Support for richer context signals such as time of day, activity, or device location.
  \item Deeper social features such as collaborative playlist editing and comments.
  \item Enhanced explainability for recommendations (e.g., showing why a song was recommended).
\end{itemize}

\end{document}
